Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-03-31 paper.tex
add vim modeline and expand opening quote

\title{Sailing the High Seas:\\ A Christian exploration of piracy}
\author{Pedro J. Avalos Jim\'enez, Niklas Anderson}
\date{Wheaton College\\\today}

@@

\begin{displayquote}
  \textins{T}he air in which we breathe, move, and have our physical being, incapable of
  confinement or exclusive appropriation. Inventions then cannot, in nature, be
  a subject of property.~\cite{barlow:wine}
\end{displayquote}

@@

>>>>

\title{Sailing the High Seas:\\ A Christian Exploration of Piracy}
\author{Pedro J. Avalos Jim\'enez, Niklas Anderson}
\date{Wheaton College\\\today}

@@

\begin{displayquote}
  \textins That ideas should freely spread from one to another over the globe, for the
    moral and mutual instruction of man, and improvement of his condition, seems to have been
    peculiarly and benevolently designed by nature, when she made them, like fire, expansible
    over all space, without lessening their density at any point, and like the air in which we
    breathe, move, and have our physical being, incapable of confinement or exclusive
    appropriation. Inventions then cannot, in nature, be a subject of property.  Thomas
    Jefferson ~\cite{barlow:wine}
\end{displayquote}

@@

% vim: set ts=2 sw=2 et:
